---
title: "Prediction Presentation"
author: "Zach Dungan"
date: "2023-03-03"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a pitch for a prediction model app that lets users predict the 1/4 mile time and miles per gallon of a car based on car weight, horsepower, and displacement.

The model uses a multilinear regression function to predict both values, and the data is from the 'mtcars' dataset found in base R. 

For this presentation, the app files have been simplified to show the model here. 

## Definitions

- qsec: 1/4 mile time (how fast the car can travel a 1/4 of a mile in)
- mpg: Miles per gallon (US)
- wt: Car weight (1000 lbs)
- hp: Car gross horspower
- disp: Car displacement (cubic inches)

## The Models

```{r, echo = TRUE}
modelQsec <- lm(qsec ~ wt + hp + disp, data = mtcars)
modelMPG <- lm(mpg ~ wt + hp + disp, data = mtcars)

wtInput <- 3.5
hpInput <- 110
dispInput <- 250

modelpredQsec <- predict(modelQsec, 
                         newdata = data.frame(wt = wtInput, 
                                              hp = hpInput, 
                                              disp = dispInput))
modelpredMPG <- predict(modelMPG, 
                         newdata = data.frame(wt = wtInput, 
                                              hp = hpInput, 
                                              disp = dispInput))

```

## The Results (part one)
```{r, echo= TRUE}
modelpredQsec
modelpredMPG
```

## The Results (part two)
```{r, echo = TRUE}
wtInput <- 600
hpInput <- 80
dispInput <- 400

modelpredQsec <- predict(modelQsec, 
                         newdata = data.frame(wt = wtInput, 
                                              hp = hpInput, 
                                              disp = dispInput))
modelpredMPG <- predict(modelMPG, 
                         newdata = data.frame(wt = wtInput, 
                                              hp = hpInput, 
                                              disp = dispInput))
```

## The Results (part two)
```{r, echo = TRUE}
modelpredQsec
modelpredMPG
```

## Conclusion

Thank you!